---
title: "hlmhmm metacognition seed selection and model comparison"
output: html_notebook
---


COSAS POR HACER:
- ARREGLAR CÓDIGO QUE SELECCIONA SELECCIONA SELECCIONA SEEDS, INCLUYE LOS NIVELES DE CONFIANZA Y ORDENA LOS ESTADOS YA QUE TIENEN UNA PARTE DE LA FUNCIÓN CORRESPONDIDA REPETIDA EN CADA CHUNK.
- ARREGLAR CÓDIGO DE CONFIDENCE PARA 52, 104 Y 156 TRIALS


---------------------------------------------------------------------
---------------------------------------------------------------------
LIBRARIES
---------------------------------------------------------------------
---------------------------------------------------------------------


```{r}
library(reticulate)
use_condaenv("glmhmm")

source_python("python/glm_hmm.py")
```

```{python}
import numpy as np
import numpy.random as npr
import matplotlib.pyplot as plt
import ssm 
```

```{r}
library(tidyverse)
library(broom)
library(dplyr)
library(R.matlab)
library(cowplot)

list.files("R", full.names = TRUE) |> 
  walk(source)
```


---------------------------------------------------------------------
---------------------------------------------------------------------
SEED SELECTION AND STATES ORDERING BASED ON PRECISION
---------------------------------------------------------------------
---------------------------------------------------------------------


---------------------------------------------------------------------
All trials
---------------------------------------------------------------------


```{r}
load("RData/data_trials.RData")

load("RData/m1_s.RData")
load("RData/m2_s.RData")
load("RData/m3_s.RData")
load("RData/m4_s.RData")
```


Orders the states according to their precision (descending order of slope, so the first is always the most precise) 
```{r}
m1_prec <- m1_s %>%
  mutate(fit = list(glm_hmm_extract_best_precision(fit))) |> 
  select(-data) 

save(m1_prec, file = "RData/m1_prec.RData")

m1_prec
```

```{r}
m2_prec <- m2_s %>%
  mutate(fit = list(glm_hmm_extract_best_precision(fit))) |> 
  select(-data) 

save(m2_prec, file = "RData/m2_prec.RData")

m2_prec
```

```{r}
m3_prec <- m3_s %>%
  mutate(fit = list(glm_hmm_extract_best_precision(fit))) |> 
  select(-data) 

save(m3_prec, file = "RData/m3_prec.RData")

m3_prec
```

```{r}
m4_prec <- m4_s %>%
  mutate(fit = list(glm_hmm_extract_best_precision(fit))) |> 
  select(-data) 

save(m4_prec, file = "RData/m4_prec.RData")

m4_prec
```

Does the same and adds the confidence rating for each trial
```{r}
m1_conf_prec <- m1_s %>%
  mutate(fit = list(glm_hmm_extract_best_precision(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m1_conf_prec_w <- m1_conf_prec |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m1_conf_prec_ord <- m1_conf_prec_w |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m1_conf_prec_post_prob <- m1_conf_prec |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m1_conf_prec_post_wins <- m1_conf_prec_post_prob |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m1_conf_prec_ord) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m1_conf_prec_post_wins, file = "RData/m1_conf_prec_post_wins.RData")

m1_conf_prec_post_wins
```

```{r}
m2_conf_prec <- m2_s %>%
  mutate(fit = list(glm_hmm_extract_best_precision(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m2_conf_prec_w <- m2_conf_prec |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m2_conf_prec_ord <- m2_conf_prec_w |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m2_conf_prec_post_prob <- m2_conf_prec |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m2_conf_prec_post_wins <- m2_conf_prec_post_prob |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m2_conf_prec_ord) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m2_conf_prec_post_wins, file = "RData/m2_conf_prec_post_wins.RData")

m2_conf_prec_post_wins
```

```{r}
m3_conf_prec <- m3_s %>%
  mutate(fit = list(glm_hmm_extract_best_precision(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m3_conf_prec_w <- m3_conf_prec |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m3_conf_prec_ord <- m3_conf_prec_w |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m3_conf_prec_post_prob <- m3_conf_prec |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m3_conf_prec_post_wins <- m3_conf_prec_post_prob |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m3_conf_prec_ord) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m3_conf_prec_post_wins, file = "RData/m3_conf_prec_post_wins.RData")

m3_conf_prec_post_wins
```

```{r}
m4_conf_prec <- m4_s %>%
  mutate(fit = list(glm_hmm_extract_best_precision(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m4_conf_prec_w <- m4_conf_prec |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m4_conf_prec_ord <- m4_conf_prec_w |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m4_conf_prec_post_prob <- m4_conf_prec |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m4_conf_prec_post_wins <- m4_conf_prec_post_prob |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m4_conf_prec_ord) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m4_conf_prec_post_wins, file = "RData/m4_conf_prec_post_wins.RData")

m4_conf_prec_post_wins
```


---------------------------------------------------------------------
First 52 trials
---------------------------------------------------------------------


```{r}
load("RData/m1_s_52.RData")
load("RData/m2_s_52.RData")
load("RData/m3_s_52.RData")
load("RData/m4_s_52.RData")
```

Renames the states according to their values (so similar states between subjects can be identified)
```{r}
m1_52 <- m1_s_52 %>%
    mutate(fit = list(glm_hmm_extract_best(fit))) %>%
    order_states_glm_hmm()

m1_52

save(m1_52, file = "RData/m1_52.RData")
```

Intentando que la variable incluya la información suficiente para poder graficarla teniendo los estados ordenados
```{r}
m1_52_ex <- m1_s_52 %>%
    mutate(fit = list(glm_hmm_extract_best(fit)))  
  
  weights_glm_hmm <- m1_52_ex |> 
   unnest_wider(fit) |> 
   #select(subject, recovered_weights) |> 
   unnest(recovered_weights)

  order <- weights_glm_hmm |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) #|> 
   #select(subject, state, ordered_state)

  ordered_weights_glm_hmm <- weights_glm_hmm |> 
    left_join(order) |> 
    select(-state) |> 
    rename(state = ordered_state)

  ordered_weights_glm_hmm
  
  filled_ordered_weights_glm_hmm <- ordered_weights_glm_hmm |>
    group_by(subject) |>
    fill(state)
  
  filled_ordered_weights_glm_hmm
```


```{r}
m2_52 <- m2_s_52 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  order_states_glm_hmm()

m2_52

save(m2_52, file = "RData/m2_52.RData")
```



```{r}
m2_52_ex <- m2_s_52 %>%
    mutate(fit = list(glm_hmm_extract_best(fit)))  
  
  weights_glm_hmm_2 <- m2_52_ex |> 
   unnest_wider(fit) |> 
   #select(subject, recovered_weights) |> 
   unnest(recovered_weights)

  order_2 <- weights_glm_hmm_2 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) #|> 
   #select(subject, state, ordered_state)
  
  ordered_weights_glm_hmm_2 <- weights_glm_hmm_2 |> 
    left_join(order_2) |> 
    select(-state) |> 
    rename(state = ordered_state)
  
  ordered_weights_glm_hmm_2_ex <- ordered_weights_glm_hmm_2 |>
    group_by(subject) |>
    mutate(state = c("S1", "S1", "S2", "S2")) |>
    ungroup()

  ordered_weights_glm_hmm_2
  ordered_weights_glm_hmm_2_ex
```




```{r}
m3_52 <- m3_s_52 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  order_states_glm_hmm()

m3_52

save(m3_52, file = "RData/m3_52.RData")
```

```{r}
m4_52 <- m4_s_52 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  order_states_glm_hmm()

m4_52

save(m4_52, file = "RData/m4_52.RData")
```

```{r}
load("RData/m1_52.RData")
load("RData/m2_52.RData")
load("RData/m3_52.RData")
load("RData/m4_52.RData")
```

Does the same and adds the confidence rating for each trial
```{r}
m1_conf_52 <- m1_s_52 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m1_conf_w_52 <- m1_conf_52 |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m1_conf_ord_52 <- m1_conf_w_52 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m1_conf_post_prob_52 <- m1_conf_52 |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m1_conf_post_wins_52 <- m1_conf_post_prob_52 |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m1_conf_ord_52) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m1_conf_post_wins_52, file = "RData/m1_conf_post_wins_52.RData")
```

```{r}
m2_conf_52 <- m2_s_52 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m2_conf_w_52 <- m2_conf_52 |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m2_conf_ord_52 <- m2_conf_w_52 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m2_conf_post_prob_52 <- m2_conf_52 |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m2_conf_post_wins_52 <- m2_conf_post_prob_52 |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m2_conf_ord_52) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m2_conf_post_wins_52, file = "RData/m2_conf_post_wins_52.RData")
```

```{r}
m3_conf_52 <- m3_s_52 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m3_conf_w_52 <- m3_conf_52 |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m3_conf_ord_52 <- m3_conf_w_52 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m3_conf_post_prob_52 <- m3_conf_52 |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m3_conf_post_wins_52 <- m3_conf_post_prob_52 |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m3_conf_ord_52) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m3_conf_post_wins_52, file = "RData/m3_conf_post_wins_52.RData")
```

```{r}
m4_conf_52 <- m4_s_52 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m4_conf_w_52 <- m4_conf_52 |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m4_conf_ord_52 <- m4_conf_w_52 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m4_conf_post_prob_52 <- m4_conf_52 |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m4_conf_post_wins_52 <- m4_conf_post_prob_52 |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m4_conf_ord_52) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m4_conf_post_wins_52, file = "RData/m4_conf_post_wins_52.RData")
```


---------------------------------------------------------------------
First 104 trials
---------------------------------------------------------------------


```{r}
load("RData/m1_s_104.RData")
load("RData/m2_s_104.RData")
load("RData/m3_s_104.RData")
load("RData/m4_s_104.RData")
```

Renames the states according to their values (so similar states between subjects can be identified)
```{r}
m1_104 <- m1_s_104 %>%
    mutate(fit = list(glm_hmm_extract_best(fit))) %>%
    order_states_glm_hmm()

m1_104

save(m1_104, file = "RData/m1_104.RData")
```

```{r}
m2_104 <- m2_s_104 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  order_states_glm_hmm()

m2_104

save(m2_104, file = "RData/m2_104.RData")
```

```{r}
m3_104 <- m3_s_104 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  order_states_glm_hmm()

m3_104

save(m3_104, file = "RData/m3_104.RData")
```

```{r}
m4_104 <- m4_s_104 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  order_states_glm_hmm()

m4_104

save(m4_104, file = "RData/m4_104.RData")
```

```{r}
load("RData/m1_104.RData")
load("RData/m2_104.RData")
load("RData/m3_104.RData")
load("RData/m4_104.RData")
```

Does the same and adds the confidence rating for each trial
```{r}
m1_conf_104 <- m1_s_104 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m1_conf_w_104 <- m1_conf_104 |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m1_conf_ord_104 <- m1_conf_w_104 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m1_conf_post_prob_104 <- m1_conf_104 |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m1_conf_post_wins_104 <- m1_conf_post_prob_104 |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m1_conf_ord_104) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m1_conf_post_wins_104, file = "RData/m1_conf_post_wins_104.RData")
```

```{r}
m2_conf_104 <- m2_s_104 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m2_conf_w_104 <- m2_conf_104 |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m2_conf_ord_104 <- m2_conf_w_104 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m2_conf_post_prob_104 <- m2_conf_104 |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m2_conf_post_wins_104 <- m2_conf_post_prob_104 |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m2_conf_ord_104) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m2_conf_post_wins_104, file = "RData/m2_conf_post_wins_104.RData")
```

```{r}
m3_conf_104 <- m3_s_104 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m3_conf_w_104 <- m3_conf_104 |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m3_conf_ord_104 <- m3_conf_w_104 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m3_conf_post_prob_104 <- m3_conf_104 |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m3_conf_post_wins_104 <- m3_conf_post_prob_104 |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m3_conf_ord_104) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m3_conf_post_wins_104, file = "RData/m3_conf_post_wins_104.RData")
```

```{r}
m4_conf_104 <- m4_s_104 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m4_conf_w_104 <- m4_conf_104 |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m4_conf_ord_104 <- m4_conf_w_104 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m4_conf_post_prob_104 <- m4_conf_104 |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m4_conf_post_wins_104 <- m4_conf_post_prob_104 |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m4_conf_ord_104) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m4_conf_post_wins_104, file = "RData/m4_conf_post_wins_104.RData")
```


---------------------------------------------------------------------
First 156 trials
---------------------------------------------------------------------


```{r}
load("RData/m1_s_156.RData")
load("RData/m2_s_156.RData")
load("RData/m3_s_156.RData")
load("RData/m4_s_156.RData")
```

Renames the states according to their values (so similar states between subjects can be identified)
```{r}
m1_156 <- m1_s_156 %>%
    mutate(fit = list(glm_hmm_extract_best(fit))) %>%
    order_states_glm_hmm()

m1_156

save(m1_156, file = "RData/m1_156.RData")
```

```{r}
m2_156 <- m2_s_156 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  order_states_glm_hmm()

m2_156

save(m2_156, file = "RData/m2_156.RData")
```

```{r}
m3_156 <- m3_s_156 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  order_states_glm_hmm()

m3_156

save(m3_156, file = "RData/m3_156.RData")
```

```{r}
m4_156 <- m4_s_156 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  order_states_glm_hmm()

m4_156

save(m4_156, file = "RData/m4_156.RData")
```

```{r}
load("RData/m1_156.RData")
load("RData/m2_156.RData")
load("RData/m3_156.RData")
load("RData/m4_156.RData")
```

Does the same and adds the confidence rating for each trial
```{r}
m1_conf_156 <- m1_s_156 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m1_conf_w_156 <- m1_conf_156 |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m1_conf_ord_156 <- m1_conf_w_156 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m1_conf_post_prob_156 <- m1_conf_156 |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m1_conf_post_wins_156 <- m1_conf_post_prob_156 |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m1_conf_ord_156) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m1_conf_post_wins_156, file = "RData/m1_conf_post_wins_156.RData")
```

```{r}
m2_conf_156 <- m2_s_156 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m2_conf_w_156 <- m2_conf_156 |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m2_conf_ord_156 <- m2_conf_w_156 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m2_conf_post_prob_156 <- m2_conf_156 |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m2_conf_post_wins_156 <- m2_conf_post_prob_156 |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m2_conf_ord_156) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m2_conf_post_wins_156, file = "RData/m2_conf_post_wins_156.RData")
```

```{r}
m3_conf_156 <- m3_s_156 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m3_conf_w_156 <- m3_conf_156 |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m3_conf_ord_156 <- m3_conf_w_156 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m3_conf_post_prob_156 <- m3_conf_156 |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m3_conf_post_wins_156 <- m3_conf_post_prob_156 |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m3_conf_ord_156) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m3_conf_post_wins_156, file = "RData/m3_conf_post_wins_156.RData")
```

```{r}
m4_conf_156 <- m4_s_156 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m4_conf_w_156 <- m4_conf_156 |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m4_conf_ord_156 <- m4_conf_w_156 |> 
   filter(coef == "V2") |> 
   group_by(subject) |> 
   arrange(desc(value), .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m4_conf_post_prob_156 <- m4_conf_156 |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m4_conf_post_wins_156 <- m4_conf_post_prob_156 |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m4_conf_ord_156) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m4_conf_post_wins_156, file = "RData/m4_conf_post_wins_156.RData")
```


---------------------------------------------------------------------
---------------------------------------------------------------------
SEED SELECTION AND STATES ORDERING BASED ON bias
---------------------------------------------------------------------
---------------------------------------------------------------------


Seed selection and state ordering based on bias
```{r}
m1_bias <- m1_s %>%
  mutate(fit = list(glm_hmm_extract_best_bias(fit))) |> 
  select(-data) 

save(m1_bias, file = "RData/m1_bias.RData")

m1_bias
```

```{r}
m2_bias <- m2_s %>%
  mutate(fit = list(glm_hmm_extract_best_bias(fit))) |> 
  select(-data) 

save(m2_bias, file = "RData/m2_bias.RData")

m2_bias
```

```{r}
m3_bias <- m3_s %>%
  mutate(fit = list(glm_hmm_extract_best_bias(fit))) |> 
  select(-data) 

save(m3_bias, file = "RData/m3_bias.RData")

m3_bias
```

```{r}
m4_bias <- m4_s %>%
  mutate(fit = list(glm_hmm_extract_best_bias(fit))) |> 
  select(-data) 

save(m4_bias, file = "RData/m4_bias.RData")

m4_bias
```

Same for confidence
```{r}
m1_conf_bias <- m1_s %>%
  mutate(fit = list(glm_hmm_extract_best_bias(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m1_conf_bias_w <- m1_conf_bias |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m1_conf_bias_ord <- m1_conf_bias_w |> 
   filter(coef == "V1") |> 
   group_by(subject) |> 
   arrange(value, .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m1_conf_bias_post_prob <- m1_conf_bias |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m1_conf_bias_post_wins <- m1_conf_bias_post_prob |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m1_conf_bias_ord) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m1_conf_bias_post_wins, file = "RData/m1_conf_bias_post_wins.RData")

m1_conf_bias_post_wins
```

```{r}
m2_conf_bias <- m2_s %>%
  mutate(fit = list(glm_hmm_extract_best_bias(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m2_conf_bias_w <- m2_conf_bias |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m2_conf_bias_ord <- m2_conf_bias_w |> 
   filter(coef == "V1") |> 
   group_by(subject) |> 
   arrange(value, .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m2_conf_bias_post_prob <- m2_conf_bias |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m2_conf_bias_post_wins <- m2_conf_bias_post_prob |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m2_conf_bias_ord) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m2_conf_bias_post_wins, file = "RData/m2_conf_bias_post_wins.RData")

m2_conf_bias_post_wins
```

```{r}
m3_conf_bias <- m3_s %>%
  mutate(fit = list(glm_hmm_extract_best_bias(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m3_conf_bias_w <- m3_conf_bias |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m3_conf_bias_ord <- m3_conf_bias_w |> 
   filter(coef == "V1") |> 
   group_by(subject) |> 
   arrange(value, .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m3_conf_bias_post_prob <- m3_conf_bias |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m3_conf_bias_post_wins <- m3_conf_bias_post_prob |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m3_conf_bias_ord) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m3_conf_bias_post_wins, file = "RData/m3_conf_bias_post_wins.RData")

m3_conf_bias_post_wins
```

```{r}
m4_conf_bias <- m4_s %>%
  mutate(fit = list(glm_hmm_extract_best_bias(fit))) |> 
  select(-data) |> 
  unnest_wider(fit)

m4_conf_bias_w <- m4_conf_bias |> 
  select(subject, recovered_weights) |> 
  unnest(recovered_weights)

m4_conf_bias_ord <- m4_conf_bias_w |> 
   filter(coef == "V1") |> 
   group_by(subject) |> 
   arrange(value, .by_group = TRUE) |> 
   mutate(ordered_state = paste0("S", row_number())) |> 
   select(subject, state, ordered_state)

m4_conf_bias_post_prob <- m4_conf_bias |> 
  select(subject, posterior_probs) |> 
  unnest(posterior_probs)

m4_conf_bias_post_wins <- m4_conf_bias_post_prob |> 
  group_by(subject, trial) %>%
  filter(p == max(p)) %>%
  select(-p) |> 
  left_join(m4_conf_bias_ord) |> 
  select(-state) |> 
  rename(state = ordered_state) |> 
  left_join(data_trials, 
            by = join_by(subject, trial))

save(m4_conf_bias_post_wins, file = "RData/m4_conf_bias_post_wins.RData")

m4_conf_bias_post_wins
```


---------------------------------------------------------------------
---------------------------------------------------------------------
MODEL COMPARISON OF MODELS ORDERED BY PRECISION
---------------------------------------------------------------------
---------------------------------------------------------------------


---------------------------------------------------------------------
All trials
---------------------------------------------------------------------


liks for each model
```{r}
liks_m1 <- m1_s %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 1")

liks_m2 <- m2_s %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 2")

liks_m3 <- m3_s %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 3")

liks_m4 <- m4_s %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 4")

save(liks_m1, file = "RData/liks_m1.RData")
save(liks_m2, file = "RData/liks_m2.RData")
save(liks_m3, file = "RData/liks_m3.RData")
save(liks_m4, file = "RData/liks_m4.RData")
```

```{r}
load("RData/liks_m1.RData")
load("RData/liks_m2.RData")
load("RData/liks_m3.RData")
load("RData/liks_m4.RData")
```

Calculates the number of subjects for which each model fits the best
```{r}
liks_all <- liks_m1 |> 
  bind_rows(liks_m2) |> 
  bind_rows(liks_m3) |> 
  bind_rows(liks_m4) |>
  mutate(aic = -2 * log_lik + 2 *n_par)

save(liks_all, file = "RData/liks_all.RData")

liks_all_best <- liks_all |> 
  group_by(subject) |> 
  filter(aic == min(aic)) 

liks_all_best |> 
  ungroup() |> 
  count(model)

save(liks_all_best, file = "RData/liks_all_best.RData")
```


---------------------------------------------------------------------
First 52 trials
---------------------------------------------------------------------


liks for each model
```{r}
liks_m1_52 <- m1_s_52 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 1")

liks_m2_52 <- m2_s_52 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 2")

liks_m3_52 <- m3_s_52 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 3")

liks_m4_52 <- m4_s_52 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 4")

save(liks_m1_52, file = "RData/liks_m1_52.RData")
save(liks_m2_52, file = "RData/liks_m2_52.RData")
save(liks_m3_52, file = "RData/liks_m3_52.RData")
save(liks_m4_52, file = "RData/liks_m4_52.RData")
```

```{r}
load("RData/liks_m1_52.RData")
load("RData/liks_m2_52.RData")
load("RData/liks_m3_52.RData")
load("RData/liks_m4_52.RData")
```

Calculates the number of subjects for which each model fits the best
```{r}
liks_52 <- liks_m1_52 |> 
  bind_rows(liks_m2_52) |> 
  bind_rows(liks_m3_52) |> 
  bind_rows(liks_m4_52) |>
  mutate(aic = -2 * log_lik + 2 *n_par)

save(liks_all, file = "RData/liks_52.RData")

liks_52_best <- liks_52 |> 
  group_by(subject) |> 
  filter(aic == min(aic)) 

liks_52_best |> 
  ungroup() |> 
  count(model)

save(liks_52_best, file = "RData/liks_52_best.RData")
```


---------------------------------------------------------------------
First 104 trials
---------------------------------------------------------------------


liks for each model
```{r}
liks_m1_104 <- m1_s_104 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 1")

liks_m2_104 <- m2_s_104 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 2")

liks_m3_104 <- m3_s_104 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 3")

liks_m4_104 <- m4_s_104 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 4")

save(liks_m1_104, file = "RData/liks_m1_104.RData")
save(liks_m2_104, file = "RData/liks_m2_104.RData")
save(liks_m3_104, file = "RData/liks_m3_104.RData")
save(liks_m4_104, file = "RData/liks_m4_104.RData")
```

```{r}
load("RData/liks_m1_104.RData")
load("RData/liks_m2_104.RData")
load("RData/liks_m3_104.RData")
load("RData/liks_m4_104.RData")
```

Calculates the number of subjects for which each model fits the best
```{r}
liks_104 <- liks_m1_104 |> 
  bind_rows(liks_m2_104) |> 
  bind_rows(liks_m3_104) |> 
  bind_rows(liks_m4_104) |>
  mutate(aic = -2 * log_lik + 2 *n_par)

save(liks_all, file = "RData/liks_104.RData")

liks_104_best <- liks_104 |> 
  group_by(subject) |> 
  filter(aic == min(aic)) 

liks_104_best |> 
  ungroup() |> 
  count(model)

save(liks_104_best, file = "RData/liks_104_best.RData")
```


---------------------------------------------------------------------
First 156 trials
---------------------------------------------------------------------


liks for each model
```{r}
liks_m1_156 <- m1_s_156 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 1")

liks_m2_156 <- m2_s_156 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 2")

liks_m3_156 <- m3_s_156 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 3")

liks_m4_156 <- m4_s_156 %>%
  mutate(fit = list(glm_hmm_extract_best(fit))) %>%
  unnest_wider(fit) %>%
  mutate(n = map(data, count)) %>%
  unnest(n) %>%
  select(subject, log_lik, n_par, n) %>%
  mutate(model = "int-slo 4")

save(liks_m1_156, file = "RData/liks_m1_156.RData")
save(liks_m2_156, file = "RData/liks_m2_156.RData")
save(liks_m3_156, file = "RData/liks_m3_156.RData")
save(liks_m4_156, file = "RData/liks_m4_156.RData")
```

```{r}
load("RData/liks_m1_156.RData")
load("RData/liks_m2_156.RData")
load("RData/liks_m3_156.RData")
load("RData/liks_m4_156.RData")
```

Calculates the number of subjects for which each model fits the best
```{r}
liks_156 <- liks_m1_156 |> 
  bind_rows(liks_m2_156) |> 
  bind_rows(liks_m3_156) |> 
  bind_rows(liks_m4_156) |>
  mutate(aic = -2 * log_lik + 2 *n_par)

save(liks_all, file = "RData/liks_156.RData")

liks_156_best <- liks_156 |> 
  group_by(subject) |> 
  filter(aic == min(aic)) 

liks_156_best |> 
  ungroup() |> 
  count(model)

save(liks_156_best, file = "RData/liks_156_best.RData")
```

