---
title: "glmhmm metacognition"
output: html_notebook
---


---------------------------------------------------------------------
---------------------------------------------------------------------
LIBRARIES AND FUNCTIONS
---------------------------------------------------------------------
---------------------------------------------------------------------


```{r}
library(reticulate)
use_condaenv("glmhmm")

source_python("python/glm_hmm.py")
```

```{python}
import numpy as np
import numpy.random as npr
import matplotlib.pyplot as plt
import ssm 
```

```{r}
library(tidyverse)
library(broom)
library(dplyr)
library(R.matlab)
library(cowplot)

list.files("R", full.names = TRUE) |> 
  walk(source)
```


----------------------------------------------------------------------
Download of data
----------------------------------------------------------------------

- stimulus refers to which group of dots (right or left) has more of them (check; the quantity of trials with more dots either on the left or right group varies from subject to subject).
- dot_diff is the difference of dots between stimuli (subject where asked which stimulus had more dots).
- confidence is the confidence scale meassured with a 11-point probabilistic 
rating scale (1=certainly wrong, 3=probably wrong, 5=maybe wrong, 7=maybe correct, 9=probably correct, 11=certainly correct)

```{r}
data_trials <- read_csv("data/data_Rouault_2018_Expt1.csv", show_col_types = FALSE) 
data_trials <- rename(data_trials, subject = Subj_idx, stimulus = Stimulus, response = Response, confidence = Confidence, RT = RT_dec, dot_diff = DotDiff, correct = Accuracy)

data_trials_52 <- data_trials |>
  group_by(subject) |>
  mutate(trial = row_number()) |>
  filter(trial <= 52) |> 
  mutate(stimulus = if_else(stimulus == 0, -1, 1), 
         dot_diff = stimulus * dot_diff) 
  
design_matrix_52 <- data_trials_52 %>%
  mutate(session = 1, 
         intercept = 1, 
         dot_diff = dot_diff) %>% 
  ungroup() %>% 
  select(subject, session, response, intercept, dot_diff) 

design_matrix_52
```


----------------------------------------------------------------------
Modify number of seeds
----------------------------------------------------------------------


```{r}
n_seeds <- 20
```


----------------------------------------------------------------------
----------------------------------------------------------------------
MODELS:
----------------------------------------------------------------------
----------------------------------------------------------------------


----------------------------------------------------------------------
1S
----------------------------------------------------------------------


```{r}
glm_hmm1_seeds_52 <- design_matrix_52 |> 
  group_by(subject) |> 
  nest() %>%
  rowwise() %>%
  mutate(fit = list(glm_hmm_r(data, 
                              .num_states = 1, .seeds = 1:n_seeds,
                              .all_seeds = TRUE)))
```


```{r}
save(glm_hmm1_seeds_52, file = "RData/glm_hmm1_seeds_52.RData")
```


---------------------------------------------------------------------
2S 
---------------------------------------------------------------------


```{r}
glm_hmm2_seeds_52 <- design_matrix_52 |> 
  group_by(subject) |> 
  nest() %>%
  rowwise() %>%
  mutate(fit = list(glm_hmm_r(data, 
                              .num_states = 2, .seeds = 1:n_seeds,
                              .all_seeds = TRUE)))
```


```{r}
save(glm_hmm2_seeds_52, file = "RData/glm_hmm2_seeds_52.RData")
```

---------------------------------------------------------------------
3S 
---------------------------------------------------------------------


```{r}
glm_hmm3_seeds_52 <- design_matrix_52 |> 
  group_by(subject) |> 
  nest() %>%
  rowwise() %>%
  mutate(fit = list(glm_hmm_r(data, 
                              .num_states = 3, .seeds = 1:n_seeds,
                              .all_seeds = TRUE)))
```


```{r}
save(glm_hmm3_seeds_52, file = "RData/glm_hmm3_seeds_52.RData")
```

---------------------------------------------------------------------
4S 
---------------------------------------------------------------------


```{r}
glm_hmm4_seeds_52 <- design_matrix_52 |> 
  group_by(subject) |> 
  nest() %>%
  rowwise() %>%
  mutate(fit = list(glm_hmm_r(data, 
                              .num_states = 4, .seeds = 1:n_seeds,
                              .all_seeds = TRUE)))
```


```{r}
save(glm_hmm4_seeds_52, file = "RData/glm_hmm4_seeds_52.RData")
```

