---
title: "glmhmm metacognition plots"
output: html_notebook
---

```{r}
library(reticulate)
use_condaenv("glmhmm")

source_python("python/glm_hmm.py")
```

```{python}
import numpy as np
import numpy.random as npr
import matplotlib.pyplot as plt
import ssm 
```

```{r}
library(tidyverse)
library(broom)
library(dplyr)
library(R.matlab)
library(cowplot)
library(flexplot)
library(ggforce)

list.files("R", full.names = TRUE) |> 
  walk(source)
```


----------------------------------------------------------------------
----------------------------------------------------------------------
INDIVIDUAL MODEL PLOTTING
----------------------------------------------------------------------
----------------------------------------------------------------------


```{r}
load("RData/data_trials.RData")
```

```{r}
load("RData/m1_fit.RData")
# load("RData/m1_52.RData")
# load("RData/m1_104.RData")
# load("RData/m1_156.RData")

load("RData/m2_fit.RData")
# load("RData/m2_52.RData")
# load("RData/m2_104.RData")
# load("RData/m2_156.RData")

load("RData/m3_fit.RData")
# load("RData/m3_52.RData")
# load("RData/m3_104.RData")
# load("RData/m3_156.RData")

load("RData/m4_fit.RData")
# load("RData/m4_52.RData")
# load("RData/m4_104.RData")
# load("RData/m4_156.RData")
```

Plotting one state:
```{r}
plots_1 <- m1_fit[m1_fit$subject %in% unique(m1_fit$subject)[1:10], ] %>% 
    rowwise() %>% 
    mutate(p = list(plotting_one_participant(fit, subject)))
  
plots_1_grid <- plot_grid(plotlist = plots_1$p, ncol = 2)
  
file_name <- paste0("figures/", deparse(substitute(.glm_hmm)), ".pdf")

ggsave("figures/plots_1_grid.pdf",
       plots_1_grid, width = 15, height = 15)
```

Plotting two states:
```{r}
plots_2 <- m2_fit[m2_fit$subject %in% unique(m2_fit$subject)[1:10], ] %>% 
    rowwise() %>% 
    mutate(p = list(plotting_one_participant(fit, subject)))
  
plots_2_grid <- plot_grid(plotlist = plots_2$p, ncol = 2)
  
file_name <- paste0("figures/", deparse(substitute(.glm_hmm)), ".pdf")
  
ggsave("figures/plots_2_grid.pdf", 
       plots_2_grid, width = 15, height = 15)
```

Plotting three states:
```{r}
plots_3 <- m3_fit[m3_fit$subject %in% unique(m3_fit$subject)[1:10], ] %>% 
    rowwise() %>% 
    mutate(p = list(plotting_one_participant(fit, subject)))
  
plots_3_grid <- plot_grid(plotlist = plots_3$p, ncol = 2)
  
file_name <- paste0("figures/", deparse(substitute(.glm_hmm)), ".pdf")
  
ggsave("figures/plots_3_grid.pdf", 
       plots_3_grid, width = 15, height = 15)
```

Plotting four states:
```{r}
plots_4 <- m4_fit[m4_fit$subject %in% unique(m4_fit$subject)[1:10], ] %>% 
    rowwise() %>% 
    mutate(p = list(plotting_one_participant(fit, subject)))
  
plots_4_grid <- plot_grid(plotlist = plots_4$p, ncol = 2)
  
file_name <- paste0("figures/", deparse(substitute(.glm_hmm)), ".pdf")
  
ggsave("figures/plots_4_grid.pdf", 
       plots_4_grid, width = 15, height = 15)
```


----------------------------------------------------------------------
----------------------------------------------------------------------
SUBJECT DISTRIBUTION OF BEST MODEL 
----------------------------------------------------------------------
----------------------------------------------------------------------


```{r}
load("RData/liks_all_best.RData")
load("RData/liks_52_best.RData")
load("RData/liks_104_best.RData")
load("RData/liks_156_best.RData")
```

Including all trials
```{r}
plot_dist_best <- flexplot(model~1, liks_all_best) +
  ggtitle("Best model subject count") +
  scale_x_discrete(labels = c("1 state", "2 states", "3 states", "4 states"))

plot_dist_best

ggsave("figures/plot_dist_best.pdf")
```

First 52 trials
```{r}
plot_dist_best_52 <- flexplot(model~1, liks_52_best) +
  ggtitle("Best model subject count") +
  scale_x_discrete(labels = c("1 state", "2 states", "3 states", "4 states"))

plot_dist_best_52

ggsave("figures/plot_dist_best_52.pdf")
```

First 104 trials
```{r}
plot_dist_best_104 <- flexplot(model~1, liks_104_best) +
  ggtitle("Best model subject count") +
  scale_x_discrete(labels = c("1 state", "2 states", "3 states", "4 states"))

plot_dist_best_104

ggsave("figures/plot_dist_best_104.pdf")
```

First 156 trials
```{r}
plot_dist_best_156 <- flexplot(model~1, liks_156_best) +
  ggtitle("Best model subject count") +
  scale_x_discrete(labels = c("1 state", "2 states", "3 states", "4 states"))

plot_dist_best_156

ggsave("figures/plot_dist_best_156.pdf")
```


----------------------------------------------------------------------
----------------------------------------------------------------------
DWELL TIME DISTRIBUTION
----------------------------------------------------------------------
----------------------------------------------------------------------


```{r}
load("RData")
```



----------------------------------------------------------------------
----------------------------------------------------------------------
CONFIDENCE
----------------------------------------------------------------------
----------------------------------------------------------------------


----------------------------------------------------------------------
States ordered based on precision
----------------------------------------------------------------------


```{r}
load("RData/m1_conf_prec.RData")
# load("RData/m1_conf_52.RData")
# load("RData/m1_conf_104.RData")
# load("RData/m1_conf_156.RData")

load("RData/m2_conf_prec.RData")
# load("RData/m2_conf_52.RData")
# load("RData/m2_conf_104.RData")
# load("RData/m2_conf_156.RData")

load("RData/m3_conf_prec.RData")
# load("RData/m3_conf_52.RData")
# load("RData/m3_conf_104.RData")
# load("RData/m3_conf_156.RData")

load("RData/m4_conf_prec.RData")
# load("RData/m4_conf_52.RData")
# load("RData/m4_conf_104.RData")
# load("RData/m4_conf_156.RData")
```

```{r}
load("RData/m1_conf_prec_sub.RData")
load("RData/m2_conf_prec_sub.RData")
load("RData/m3_conf_prec_sub.RData")
load("RData/m4_conf_prec_sub.RData")
```

Define a custom function to calculate the confidence interval
```{r}
calculate_ci <- function(x) {
  mean_val <- mean(x)
  n <- length(x)
  se <- sd(x) / sqrt(n)
  margin_error <- qt(0.975, df = n - 1) * se
  ci_inf <- mean_val - margin_error
  ci_sup <- mean_val + margin_error
  return(as.numeric(c(ci_inf, ci_sup)))
}
```

1S model:
CREO QUE HAY ALGO MAL EN EL CÃLCULO DE LOS CIS.
```{r}
n_m1_prec <- length(m1_conf_prec_sub)
se_m1_prec <- mean(m1_conf_prec_sub$sd_confidence / sqrt(n_m1_prec))
margin_error_m1_prec <- mean(qt(0.975, df = n_m1_prec - 1) * se_m1_prec)
ci_inf_m1_prec <- mean(m1_conf_prec_sub$mean_confidence - margin_error_m1_prec)
ci_sup_m1_prec <- mean(m1_conf_prec_sub$mean_confidence + margin_error_m1_prec)
mean_m1_prec <- mean(m1_conf_prec_sub$mean_confidence)

means_conf_prec_m1_plot <- ggplot() +
  geom_sina(data = m1_conf_prec_sub, aes(x = 1, y = mean_confidence), binwidth = .02, maxwidth = .5, size = .75) +
  geom_crossbar(size = .10, width = 0.2, aes(x = 1, y = mean_m1_prec, ymin = ci_inf_m1_prec, ymax = ci_sup_m1_prec)) +
  labs(x = " ", y = "Confidence") +
  theme_classic() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.title.x = element_blank(),
           axis.line = element_line(size = .25), 
         axis.ticks = element_line(size = .25))

ggsave("figures/means_conf_prec_m1_plot.pdf")

means_conf_prec_m1_plot
```

2S model:
(Subject 11 had a mean confidience of 11 and a sd of 0)
```{r}
means_conf_prec_m2 <- aggregate(mean_confidence ~ state, data = m2_conf_prec_sub, FUN = mean)
ci_conf_prec_m2 <- aggregate(mean_confidence ~ state, data = m2_conf_prec_sub, FUN = function(x) t.test(x)$conf.int)

result_conf_prec_2S <- merge(means_conf_prec_m2, ci_conf_prec_m2, by = "state")

means_conf_prec_m2_plot <- ggplot() +
  geom_sina(data = m2_conf_prec_sub, aes(x = state, y = mean_confidence), binwidth = .02, maxwidth = .5, size = .50) +
  geom_crossbar(data = result_conf_prec_2S, size = .30, width = 0.5, aes(x = state, y = mean_confidence.x, ymin = mean_confidence.y[,1], ymax = mean_confidence.y[,2], color = state)) +
  labs(x = "State", y = "Confidence") +
  theme_classic() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.title.x = element_blank(),
           axis.line = element_line(size = .25), 
         axis.ticks = element_line(size = .25))

ggsave("figures/means_conf_prec_m2_plot.pdf")

means_conf_prec_m2_plot
```

3S model:
```{r}
ci_conf_prec_m3 <- sapply(
  split(m3_conf_prec_sub$mean_confidence, m3_conf_prec_sub$state),
  function(x) {
    result <- calculate_ci(x)
    print(result)
    result
  }
)
ci_conf_prec_m3 <- t(ci_conf_prec_m3)

ci_conf_prec_m3 <- data.frame(
  state = rownames(ci_conf_prec_m3),
  ci_inf = ci_conf_prec_m3[, 1],
  ci_sup = ci_conf_prec_m3[, 2]
)

# Create a new dataframe with group, mean, and confidence intervals
result_conf_prec_3S <- as.data.frame(ci_conf_prec_m3) |>
  group_by(state) |>
  mutate(mean = (ci_inf + ci_sup)/2)

result_conf_prec_3S

means_conf_prec_m3_plot <- ggplot() +
  geom_sina(data = m3_conf_prec_sub, aes(x = state, y = mean_confidence), binwidth = .02, maxwidth = .5, size = .50) +
  geom_crossbar(data = result_conf_prec_3S, size = .30, width = 0.5, aes(x = state, y = mean, ymin = ci_inf, ymax = ci_sup, color = state)) +
  labs(x = "State", y = "Confidence") +
  theme_classic() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.title.x = element_blank(),
           axis.line = element_line(size = .25), 
         axis.ticks = element_line(size = .25))

ggsave("figures/means_conf_prec_m3_plot.pdf")

means_conf_prec_m3_plot
```

4S model:
```{r}
ci_conf_prec_m4 <- sapply(
  split(m4_conf_prec_sub$mean_confidence, m4_conf_prec_sub$state),
  function(x) {
    result <- calculate_ci(x)
    print(result)
    result
  }
)
ci_conf_prec_m4 <- t(ci_conf_prec_m4)

ci_conf_prec_m4 <- data.frame(
  state = rownames(ci_conf_prec_m4),
  ci_inf = ci_conf_prec_m4[, 1],
  ci_sup = ci_conf_prec_m4[, 2]
)

# Create a new dataframe with group, mean, and confidence intervals
result_conf_prec_4S <- as.data.frame(ci_conf_prec_m4) |>
  group_by(state) |>
  mutate(mean = (ci_inf + ci_sup)/2)

result_conf_prec_4S

means_conf_prec_m4_plot <- ggplot() +
  geom_sina(data = m4_conf_prec_sub, aes(x = state, y = mean_confidence), binwidth = .02, maxwidth = .5, size = .50) +
  geom_crossbar(data = result_conf_prec_4S, size = .30, width = 0.5, aes(x = state, y = mean, ymin = ci_inf, ymax = ci_sup, color = state)) +
  labs(x = "State", y = "Confidence") +
  theme_classic() +
   theme(legend.position = "none",
     strip.background = element_blank(),
     axis.title.x = element_blank(),
           axis.line = element_line(size = .25), 
         axis.ticks = element_line(size = .25))

ggsave("figures/means_conf_prec_m4_plot.pdf")

means_conf_prec_m4_plot
```


----------------------------------------------------------------------
States ordered based on bias
----------------------------------------------------------------------


```{r}
load("RData/m1_conf_bias_sub.RData")
load("RData/m2_conf_bias_sub.RData")
load("RData/m3_conf_bias_sub.RData")
load("RData/m4_conf_bias_sub.RData")
```








